\documentclass[10pt,letterpaper]{article}
\usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage[round,authoryear]{natbib}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\title{\vspace*{-0.8in}\textbf{Response to Reviewers --- Second Revision}}
\author{}
\date{}

\begin{document}
\maketitle

\noindent\textbf{Manuscript:} A Four-Dimension Pre-Modeling Audit Protocol for Educational Prediction Benchmarks\\
\textbf{Journal:} Scientific Reports\\
\textbf{Revision:} Second round

\vspace{0.2in}
\noindent Dear Editor and Reviewers,

We thank the reviewers for their careful reading of our revised manuscript. Below we address each remaining comment point by point. All changes are described with specific line references.

\section*{Response to Reviewer 1}

\textbf{Recommendation:} Accept with minor suggestion.

\textbf{Comment:} The authors may wish to cite Saşmaz (2026), which uses a multi-model machine learning framework on PISA 2022 data and is relevant to the benchmarking methodology discussed here.

\textbf{Response:} We thank the reviewer for this helpful suggestion and have added \citet{Sasmaz2026} to the Discussion section (lines~351--352). The citation positions our audit as complementary to multi-model benchmarking approaches such as the one demonstrated by \citet{Sasmaz2026} on PISA 2022 data: while such frameworks establish strong predictive baselines across model families, the pre-modeling audit proposed here adds a structural reliability check that can precede and inform such comparisons.

\section*{Response to Reviewer 2}

\textbf{Recommendation:} Minor revision (second round).

\vspace{0.2in}
\noindent We thank Reviewer~2 for the close reading and for pushing us to clarify four important points.

\subsection*{Comment 2-1: Feature set alignment for fair retention-ratio calculation}

\textbf{Reviewer:} The retention ratio currently compares group-holdout $R^2$ (with group identifiers excluded) against iid $R^2$ (with group identifiers included). This asymmetry needs to be addressed.

\textbf{Response:} We agree and have made the following changes:

\begin{itemize}
  \item Modified \texttt{run\_7dataset\_audit.py} (lines~226--234) to run IID splits on the same clean feature matrix (group-identifier columns excluded) when the adapter reports such columns. The clean iid $R^2$ is stored as \texttt{iid\_r2\_clean} in the output profile.
  \item Updated the retention-ratio logic (line~337) to use \texttt{iid\_r2\_clean} when available, ensuring apples-to-apples comparison.
  \item Re-ran the full pipeline and updated all affected numbers:
    \begin{itemize}
      \item xAPI-Edu: iid $R^2$ 0.599 $\to$ 0.614, retention 81\% $\to$ 79\% (profile unchanged: Strong)
      \item UCI Student: iid $R^2$ 0.262 $\to$ 0.242, retention $-37\%$ $\to$ $-40\%$ (profile unchanged: Mostly Passing)
      \item Entrance Exam: iid $R^2$ unchanged at 0.438 (board features have negligible impact on iid performance)
    \end{itemize}
  \item Updated all affected numbers in the main text (xAPI-Edu 0.614, UCI Student 0.242, retention ratios 79\% and $-40\%$).
  \item Removed stale values (0.599, 0.262, 81\%, $-37\%$) from the manuscript.
  \item Updated \texttt{results/audit\_7dataset\_results.json} with the corrected canonical values.
  \item Regenerated all figures.
\end{itemize}

No profile boundaries were crossed for any dataset, and the three key substantive conclusions remain unchanged.

\subsection*{Comment 2-2: Structural versus model-dependent fragility}

\textbf{Reviewer:} Ridge and ensemble models recover group-holdout performance for Entrance Exam. Failure of the unregularized linear model alone is insufficient to establish structural fragility. Persistent failures across model families should be distinguished from model-dependent or partly remediable failures.

\textbf{Response:} We fully agree and have revised the manuscript throughout to draw this distinction clearly:

\begin{itemize}
  \item \textbf{Finding~1} (line~333): Now explicitly distinguishes ``structural fragility'' (Higher Ed: all models $R^2 < -8$; UCI Student: linear $-0.097$, RF $0.018$, GBT $-0.057$) from ``linear-model-only failure that is partly remediable by ensemble models'' (Entrance Exam: RF $R^2 \approx 0.32$ vs. linear $-0.060$).
  \item \textbf{Finding~2} (line~335): Retitled to ``Structural fragility persists across model families, while model-dependent failures are partly remediable.'' Includes Entrance Exam's ensemble recovery as a counterexample.
  \item \textbf{Finding~4} (line~339): Now notes that Entrance Exam's iid-to-group gap is ``partly closed by ensemble models.''
  \item \textbf{Conclusion~(1)} (line~369): Separates structural collapse from model-dependent failure.
  \item \textbf{Conclusion~(2)} (line~371): Retitled from ``Fragility persists across model families'' to ``Structural collapse versus model-dependent failure.''
  \item \textbf{Detailed-results section} (line~194): Adds sentence: ``The nature of the failure differs: UCI Student and Higher Ed exhibit structural fragility (all model families collapse), whereas Entrance Exam's failure is linear-model-specific and partly remediable---its RF group $R^2$ reaches approximately $0.32$.''
  \item \textbf{Table~1 caption} (line~188): Replaced ``flags the structural fragility of the base benchmark'' with language describing the audit's role as flagging the weakest link, with the detailed breakdown distinguishing structurally invariant collapse from model-dependent failure.
  \item \textbf{Line~260}: Replaced ``fragile or partially fragile datasets'' with ``datasets with metadata-adequacy failures'' and annotated each dataset's failure pattern.
  \item Remaining uses of ``fragility'' in the abstract and general discussion are retained as high-level descriptors of the cross-group generalization failure phenomenon.
\end{itemize}

\subsection*{Comment 2-3: Feature-attribution scope limitation}

\textbf{Reviewer:} The feature-attribution analysis is computed under iid splits only. The connections drawn to audit dimensions are interesting but not directly supported. Either compute group-aware attributions or clearly limit scope.

\textbf{Response:} We have chosen to clearly limit the scope rather than write new group-aware attribution code. At the end of the feature-attribution section (line~322), we added:

\emph{``We note that this feature-attribution analysis is conducted under iid random splits and does not directly evaluate attribution stability under group-aware holdout; the connections drawn to the audit profiles describe the alignment between split-level attribution stability and dataset readiness rather than establishing a causal link to cross-group behavior.''}

\subsection*{Comment 2-4: RF importance type and feature-name mapping}

\textbf{Reviewer:} (a) Report the type of feature importance used (impurity-based or permutation-based). (b) Add a table mapping feature codes to meaningful names.

\textbf{Response:} (a) In the feature-attribution section (line~318), we now specify: ``Random Forest feature importances (impurity-based, using scikit-learn's default \texttt{feature\_importances\_}).'' 

(b) We added a new Supplementary Table~S7 (page~9 of the supplementary PDF) mapping all feature codes (e.g., f5, f28, f3) used in Tables~S5--S6 to human-readable feature names for UCI Student, Higher Ed, and OULAD. The table covers every feature that appears in the top-10 coefficient and importance tables.

\section*{Response to Reviewer 3}

\textbf{Response:} We thank Reviewer~3 for the comments received. We wish to offer a brief description of our manuscript for context.

Our manuscript audits seven public educational prediction datasets using a four-dimension pre-modeling protocol (baseline gap, split instability, null separation, and metadata adequacy via group-aware holdout), with linear regression, ridge, Random Forest, and Gradient Boosting as evaluation models. It does not involve the methods or datasets described in Reviewer~3's comments, which do not appear to correspond to our submission. We therefore were unable to address those specific points in our previous revision, and we sincerely apologise for any confusion this may have caused.

Notwithstanding this, the literature on post-modeling interpretability in learning analytics---including work on counterfactual explanations and the effect of class-balancing techniques on explanation quality \citep{Cavus2024ce,Cavus2024benchmark}---is directly relevant to the downstream use of datasets like OULAD. That OULAD supports analyses as demanding as counterfactual explanation benchmarking is consistent with its Strong (4/4) audit profile in our study: datasets that fail group-aware holdout are unlikely to provide the stable distributional foundation needed for reliable post-modeling interpretability work. We have added the following sentence to the Discussion (line~351):

\emph{``That OULAD supports post-modeling interpretability analyses as demanding as counterfactual explanation benchmarking \citep{Cavus2024ce,Cavus2024benchmark} is consistent with its Strong (4/4) audit profile: datasets that fail group-aware holdout are unlikely to provide the stable distributional foundation needed for reliable post-modeling interpretability work.''}

We hope this overview is helpful and remain willing to address any comments that pertain directly to our submission.

\vspace{0.3in}
\noindent We hope these revisions fully address all remaining concerns. We are grateful for the reviewers' constructive feedback, which has substantially improved the clarity and precision of the manuscript.

\vspace{0.1in}
\noindent Respectfully,\\
Yan Ma \and Lizhuo Zhang

\newpage
\bibliographystyle{unsrtnat}
\bibliography{behavioraudit}

\end{document}
